Assessing Virulence by MCG

### 2017-07-03 doc/RMD/MCG-virulence.Rmd
update mcg-virulence figure to have common theme

```{r vis, fig.width = 5, fig.height = 3}
set.seed(2017-06-29)
ggplot(top_mcg, aes(x = MCG, y = Severity)) +
  geom_boxplot() +
  geom_point(position = position_jitter(width = 0.25), alpha = 0.5) +
  theme_bw(base_size = 16, base_family = "Helvetica") +
  theme(aspect.ratio = 1/2) +
  labs(list(
    # title = "Aggressiveness for the top 10 MCGs",
    y = "Aggressiveness",
    x = "Mycelial Compatibility Group"
    ))
```

>>>>

```{r vis, fig.width = 7, fig.height = 4}
set.seed(2017-06-29)
ggplot(top_mcg, aes(x = MCG, y = Severity)) +
  geom_boxplot() +
  geom_point(position = position_jitter(width = 0.25), alpha = 0.5) +
  scale_y_continuous(limits = c(0, NA)) +
  # scale_x_discrete(position = "top") +
  theme_bw(base_size = 16, base_family = "Helvetica") +
  theme(aspect.ratio = 1/2) +
  theme(axis.text = element_text(color = "black")) +
  # theme(axis.ticks.x = element_blank()) +
  theme(panel.grid.major = element_line(colour = "grey20")) +
  theme(panel.grid.minor = element_line(colour = "grey50")) +
  theme(panel.grid.major.x = element_blank()) +
  theme(panel.border = element_blank()) +
  labs(list(
    # title = "Aggressiveness for the top 10 MCGs",
    y = "Aggressiveness",
    x = "Mycelial Compatibility Group"
    ))
```
